Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-06-12 manuscripts/manuscript.Rmd
extending language on docker, zenodo archive

R code for implementing the dynamic programming algorithm in this context is
provided as a supplementary R package to the paper, along with scripts for replicating 
the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
a Docker container image of the software environment is also provided.

>>>>

R code for implementing the dynamic programming algorithm in this context is
provided as a supplementary R package to the paper, [@zenodo], along with scripts for replicating 
the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
a Docker container image of the software environment is also provided.

### 2015-06-12 manuscripts/supplement.Rmd
extending language on docker, zenodo archive

All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control). A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifer, doi:xxx.  (This DOI is also clearly linked from the GitHub repository).

@@

The project repository is organized as an R package.  The intent is not to provide a general-purpose software tool for this kind of analysis, but rather to rely on a standardized directory structure for representing complex projects. It is our hope that this facilates understanding, reproducibility, and further exploration of these results sensu [Gentleman & Temple Lang 2007](http://biostats.bepress.com/bioconductor/paper2/), but caution that additional software engineering would be required before any of this could be applied in a different context.  The functions provided are largely specific to the analyses presented here and may undocumented or incompletely documented.

@@

All empirical or simulated data shown in the figures can also be found as tabular .csv files in this repository.

@@

>>>>

All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control). A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifier, doi:xxx.  (This DOI is also clearly linked from the GitHub repository).

@@

The project repository is organized as an R package.  The intent is not to provide a general-purpose software tool for this kind of analysis, but rather to rely on a standardized directory structure for representing complex projects. It is our hope that this facilities understanding, reproducibility, and further exploration of these results sensu [Gentleman & Temple Lang 2004](http://biostats.bepress.com/bioconductor/paper2/), but caution that additional software engineering would be required before any of this could be applied in a different context.  The functions provided are largely specific to the analyses presented here and may undocumented or incompletely documented.

@@

All empirical or simulated data shown in the figures can also be found as tabular `.csv` files in this repository.

@@

The package DESCRIPTION file lists the software dependencies required to run the included scripts. To facilitate portability and preservation of these dependencies, we also provide a machine image with all the necessary dependencies already installed which can be run on most common computer platforms using [Docker](http://docker.com). Our Docker image, `cboettig/pdg-control` can be freely downloaded from the Docker Hub, or built using the Dockerfile included in the package repository.
